Outline flowCore paper

### 2007-12-28 paper/outline.tex
fxed typos
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/flowCore@29340 bc3139a8-67e5-0310-9ffc-ced21a209358

\author{Florian Hahne*\\
  Nolwenn LeMeur*\\
  Byron Ellis\\
  Ryan Brinkman\\
  Perry Haaland\\
  Errol Strain\\
  Deepayan Sarkar\\
  Joseph Spidlen\\
  Robert Gentleman
 }

>>>>

\author{Florian Hahne*\\
  Nolwenn LeMeur*\\
  Byron Ellis\\
  Ryan Brinkman\\
  Perry Haaland\\
  Errol Strain\\
  Deepayan Sarkar\\
  Josef Spidlen\\
  Robert Gentleman
 }
